---
title: "Project 1"
author: "Julia Nguyen"
date: "10/18/2024"
output:
  html_document:
    df_print: paged
subtitle: 'CPSC 292 Section 02'
---

## Project 1

```{r, include=TRUE}
# Loading required libraries
library(patchwork)
library(ggplot2)
library(tidyverse)
library(dplyr)
```

### Step 2


```{r, include=TRUE}
data <- read.csv("../data/data.csv", header = TRUE, sep = ",", stringsAsFactors = FALSE)


```



### Step 3: Upload your zip file containing the RMD producing two visualizations and the data set. 

contrast men over women

```{r, include=TRUE}

plot(x = data$Year, y = data$Median.weekly.earnings..in.current.dollars....Total, 
     type = "l", xlab = "Time (Year)", ylab = "Median Weekly Earnings($)", main= "Total Median Weekly Earnings over Time")

```
### Step 3: Upload your zip file containing the RMD producing two visualizations and the data set. 

```{r, include=TRUE}
data <- data.frame(
  Year = c(2021, 2021, 2022, 2022, 2023, 2023),
  Quarter = c(1, 1, 1, 1, 1, 1),
  Median_Earnings_Men = c(1200, 1250, 1300, 1350, 1400, 1450),
  Median_Earnings_Women = c(800, 850, 900, 950, 1000, 1050)
)

#organize dataset
meoww<- data %>%
  select(Year, Median_Earnings_Men, Median_Earnings_Women) %>%
  pivot_longer(cols = starts_with("Median_Earnings"), 
               names_to = "Gender", 
               values_to = "Median_Earnings")

ggplot(meoww, aes(x = factor(Year), y = Median_Earnings, fill = Gender)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  labs(title = "Comparing Median Weekly Earnings by Gender (2021-2023), Q1",
       x = "Time (Year)",
       y = "Median Weekly Earnings (in dollars)") +
  theme_minimal() +
  scale_fill_manual(values = c("Median_Earnings_Men" = "blue", "Median_Earnings_Women" = "pink")) +
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5))+
  scale_y_continuous(limits = c(0, 1600))

```
Make GRAY GRIDS prominent 

notes: 
* %>% to put one function directly as input to another function for easier readability. 

* pivot_longer() is to reshape data from a wide to short format.to make the dataset easiler to look at. variable is column and obeservation is a row

* fill is to replace NA values

* position_dodge() is used so bars don't overlap. I used it to separate categorical values (gender) and numeric values (earnings) with the same group (year). 

* theme_minimal() so my ggplot looks clean (removes gridlines, etc.)

* Scale_ is to customize the graph



### Step 4 

```{r, include=TRUE}





```

### Step 5 

```{r, include=TRUE}



```