---
title: "Assignment 1.11"
author: "Julia Nguyen"
date: "09/13/2024"
output:
  html_document:
    df_print: paged
subtitle: 'CPSC 292 Section 02'
---

### Collaboration team: 

Record who you've worked on the assignment with here. 


## Assignment 1.11 -- Lists

```{r setup, include=FALSE}
# Do not alter this section of code!
knitr::opts_chunk$set(echo = TRUE)
```

Write a R code in each chunk (gray space) that provides answers to the following questions. If any questions need direct answers, give them in regular text space (white space).

### Question 1

*What are the differences between lists and data frames? When is it best to use a list versus a data frame?*

You would use lists if you need 1) Members of different sizes, member of different classes, or both. You would use a data frame only for members of different classes. People typically use lists due to their speed. Lists can have as many members as you want and each member can be a different class, but wuthun an element, must be the same type. Data frames are limited to 2D structures and must have the same type within a column. 

### Question 2

*Create a list named my.list that contains at least three members of three different data types/classes. Include the name in the next line so that R prints the list as output.*

```{r}
my.list <- list(matrix(data = 1:9, nrow = 3, ncol= 3))
```

### Question 3

*Load the data set ability.cov and use it to perform the following:*

```{r}
data(ability.cov)
```

  a. *Write a line of code that indexes the covariance value (cov) for maze and picture.*
  
```{r}
cov_maze <- ability.cov$cov["maze","picture"]
```
  
  b. *Write another line of code that indexes the covariance value for blocks and reading.*
  
```{r}
cov_block <- ability.cov$cov["blocks","reading"]
```
  
  c. *Subset the covariance value matrix (cov) so it shows only values associated with vocab.*
  
```{r}
cov_vocab <- ability.cov$cov["vocab", ]
```

Turn in this RMD file.