---
title: "Assignment 1.6"
author: "Julia Nguyen"
date: "09/08/2023"
output:
  html_document:
    df_print: paged
subtitle: 'CPSC 292 Section 02'
---

### Collaboration team: 

Record who you've worked on the assignment with here. 


## Assignment 1.6 -- Data Types in R

```{r setup, include=FALSE}
# Do not alter this section of code!
knitr::opts_chunk$set(echo = TRUE)
```

Write a R code in each chunk (gray space) that provides answers to the following questions. If any questions need direct answers, give them in regular text space (white space).

### Question 1

*For the following inputs, list all of the atomic data types that would be appropriate to store data in R. `Appropriate' means that it retains the specific information that someone would want to keep, for example: storing the number 7 as a numeric would keep the value of 7, but storing 7 as a character would not. *

*Code an example for each.*

*Hint: vectors are stored using c()!*


  a. *The word puppy*
  
  List data types here:character
  
```{r}
dog <- "puppy"
```
  b. *The condition TRUE*
  
  List data types here:logical
  
```{r}
happy <- "TRUE"
```
  
  c. *The word h8tr*
  
  List data types here:character
  
```{r}
bad <- "h8tr"
```
  
  d. *The vector < 1, 0, 1, 0 >*
  
  List data types here:numeric, character, integer
  
```{r}
hi <- c(1, 0, 1, 0) 
```
  
  e. *The vector < 9.99, 8.37 >*
  
  List data types here:numeric
  
```{r}
cost <- c(9.99, 8.37)
```

  f. *The vector < 9 + 3i, 3i >*
  
  List data types here:complex

```{r}
imagine <- c(9 + 3i, 3i)
```

  g. *The number 16*
  
  List data types here:numeric, integer

```{r}
friends <- c(16)
```

  h. *The number 3.6*

  List data types here:numeric

```{r}
gpa <- c(3.6)
```

### Question 2

*For the following functions, what types of data do they accept as arguments and what data types do they return as values?*

*Code a working example of each.*

*Hint: look up the help documentation for each function!*

 a. `median()`
  
They accept agruments: x, na.rm= , and ... 
The data type they return as values is numeric,and logical.The input accepted is logical.  

```{r}
median <- c(1, 43, 21)
median <-  c(1, 43, 21, na.rm =FALSE)
median <- c(1, 43, 21,... = TRUE)
```

 b. `sd()`
 
They accept arguements: x, na.rm=  
The data type they return as values is numeric.
```{r}
sd <- c(1, 43, 21)
sd <-  c(1, 43, NA, 21, na.rm =TRUE)
```
 
 c. `any()`
   
They accept arguemnts: ..., and na.rm=  
The data type they return as values is logical
```{r}
any <- c(1, 43, 21,...=TRUE, FALSE)

```
 
 d. `cut()`
 
  x, breaks, labels, include.lowest, right, dig.lab, ordered_result, ...
  The data type they return as values is Character. Input accepted is numeric.
  
```{r}
data <- cut(c(1, 2, 3), breaks = 4, labels = c("low", "medium", "high", "super"))
```
 
 e. `order()`
  
  ..., x, partial, decreasing, na.last, method
  The data type they return as values is integer. Input data accepted is numeric, character, or logical. 
  
```{r}
meow <- order(c(1, 2, 3), decreasing = FALSE, na.last = TRUE, method= c("shell"))
```

### Question 3

*Run the function `is.character()` on the coded example for each answer in question 1 (give each example its own line). Explain what the output of these functions mean.*

```{r}
is.character(dog)
is.character(happy)
is.character(bad)
is.character(c(1, 0, 1, 0))
is.character(c(9.99, 8.37))
is.character(c( 9 + 3i, 3i))
is.character(16)
is.character(3.6)
```

If the output it TRUE, that means that input is a character.If it isn't a character, then it is FALSE.


Turn in this RMD file.
