---
title: "Assignment 3.4"
author: "Julia Nguyen"
date: "10/30/2024"
output:
  html_document:
    df_print: paged
subtitle: "CPSC 292 Section 02"
---

## Assignment 3.4

```{r, include=TRUE}
# Loading required libraries
library(ggplot2)
library(dplyr)
library(tidyr)
```

### Question 1

*Write a for loop that loads in each data set in the data/ folder and plots the point 1 x and y values from all 6 sets on the same plot as lines. Be sure to use base graphics and color each line separately.*

```{r, include=TRUE}

dat_files <- c("data_Unit3/dataset_1.csv", "data_Unit3/dataset_2.csv", 
               "data_Unit3/dataset_3.csv", "data_Unit3/dataset_4.csv", 
               "data_Unit3/dataset_5.csv", "data_Unit3/dataset_6.csv")


plot(NA, xlim = c(-1, 1), ylim = c(-0.5, 1), xlab = "X", ylab = "Y")

colors <- rainbow(length(dat_files))

for (i in seq_along(dat_files)) {
  data <- read.csv(dat_files[i])
  lines(data$pt1_X, data$pt1_Y, col = colors[i], type = "o", pch = 16)
}




```

### Question 2

*Repeat the process for Question 1 but use ggplot2 graphics. The data set must be in the long format and have the following column names: set_number, point, x, y, z. Plot the values of x and y for point two with a scatter plot. *


```{r, include=TRUE}

dat_files <- c("data_Unit3/dataset_1.csv", "data_Unit3/dataset_2.csv", 
               "data_Unit3/dataset_3.csv", "data_Unit3/dataset_4.csv", 
               "data_Unit3/dataset_5.csv", "data_Unit3/dataset_6.csv")
all_dat <- lapply(seq_along(dat_files), function(i) {
  dat <- read.csv(dat_files[i])
  dat$set_number <- i
  dat_long <- data.frame(set_number = i, point = 2, x = dat$pt2_X, y = dat$pt2_Y)
  return(dat_long)
})
combined_dat <- do.call(rbind, all_dat)
ggplot(combined_dat, aes(x = x, y = y, color = as.factor(set_number))) +
  geom_point() +
  labs(x = "X", y = "Y", color = "Set Number") +
  theme_minimal()



```
