---
title: "Assignment 1.5"
author: "Julia Nguyen"
date: "09/04/2024"
output:
  html_document:
    df_print: paged
subtitle: 'CPSC 292 Section 02'
---

### Collaboration team: 

Max Chen

## Assignment 1.5 -- Basic R Functions

```{r setup, include=FALSE}
# Do not alter this section of code!
knitr::opts_chunk$set(echo = TRUE)
```

Write a R code in each chunk (gray space) that provides answers to the following questions. If any questions need direct answers, give them in regular text space (white space).

### Question 1

*Command-line code that produces a search for the term “hexagon” in all R help documents. How many entries are there for help pages?*

```{r}

??hexagon

```
There are 0 entries forthe help pages. 
### Question 2

*Command-line code that retrieves the help page for the function “bquote”. How many arguments does this function take? What does it return?*

```{r}

?bquote

```
There are three arguments.It returns terms language object. 

### Question 3

*Assigns a value of 10.58e−6 to the letter b.*

```{r}

b <- 10.58e−6

```


### Question 4

*Calculates the log of 2401 in base 4.*

```{r}
log(2401 , base=4)
```

### Question 5

*Calculates the square root of 49.*

```{r}
sqrt(49)
```

### Question 6

*Calculates the mean of the following values: 10, 40, 43, 24, 50, 22, 45, 76.*

```{ r}
mean(c(10, 40, 43, 24, 50, 22, 45, 76))
```



### Question 7

*One line of code which contains a deliberate syntax error. Explain what the error is in a comment below the line and how to fix it.*

```{r}
#j -> 7
```
Error because the arrow needs to point to the object (j). The object is always the letter. Spacing is essential too. 
The right answer would be 7 -> j
Turn in this RMD file.
