---
title: "Assignment 2.1"
author: "Julia Nguyen"
date: "9/25/2024"
output:
  html_document:
    df_print: paged
subtitle: 'CPSC 292 Section 02'
---

## Assignment 2.1 

```{r, include=TRUE}
# Loading required libraries

```

All graphs should be completed with basic graphics.

### Question 1

*Load the pressure data set. Make a plot of vapor pressure in mmHg versus temperature in C of mercury. Set the axis labels and title. Make this plot using a formula structure (i.e., y~x).*

```{r, include=TRUE}
data("pressure")
plot(x = pressure$temperature, y = pressure$pressure, 
     type = "l", xlab = "Pressure (mmHg)", ylab = "Temperature(˙C)", main= "vapor pressure in mmHg versus temperature in C of mercury")
```


### Question 2

*Load the DNase data set. Make a plot of density versus concentration. Set the axis labels and title. Make the point shape dependent on Run number. Make this plot without using a formula structure.*

```{r, include=TRUE}
data("DNase")

plot(x = DNase$conc, y = DNase$density, 
    pch= as.numeric(factor(DNase$Run)), 
    xlab = "Concentration", 
    ylab = "Density",
     main = "Density vs. Concentration")




```


### Question 3

*Load the dataset Loblolly. Make a plot of height versus age of trees where data are triangle-shaped points. Color the points according to the seed number.*

```{r, include=TRUE}
data("Loblolly")
seed_colors <- rainbow(length(unique(Loblolly$Seed)))
plot(x = Loblolly$age, 
     y = Loblolly$height, 
     pch=17, 
     col= seed_colors[Loblolly$Seed], 
     xlab = "Age (year)", 
     ylab = "height(cm)", 
     main = "Heigt vs. Age of Lobolly Trees")
```