---
title: "Assignment 1.9"
author: "Julia Nguyen"
date: "09/11/2024"
output:
  pdf_document: default
  html_document:
    df_print: paged
subtitle: CPSC 292 Section 02
---

### Collaboration team: 

Record who you've worked on the assignment with here. 


## Assignment 1.9 -- Arrays

```{r setup, include=FALSE}
# Do not alter this section of code!
knitr::opts_chunk$set(echo = TRUE)
```

Write a R code in each chunk (gray space) that provides answers to the following questions. If any questions need direct answers, give them in regular text space (white space).

### Question 1

*Create a three-dimensional array using `sample()` to generate data and store it in a variable called my3Darray. (The function `sample()` can be used to generate random whole numbers from a range you specify.) *

```{r}
data <- c(4,3,2)
my3darray <- array(sample(1:10, prod(data), replace = TRUE), dim = data)
```

*Use this array to answer the following questions.*

  a. *What dimensions are your 3D array?*
  
```{r}
dim(my3darray)
```

  b. *How could you subset a part of your array to a single 2D matrix? Create a working example.*
  
```{r}
my2Dmatrix <- my3darray[, , 2]
```

### Question 2

*Create a four-dimensional array using `sample()` to generate data and store it in a variable called my4Darray.*

```{r}
dimension <- c(1,2,3,4)
my4Darray <- array(sample(1:10, prod(dimension), replace= TRUE), dim= dimension)
```

*Use this array to answer the following questions.*

  a. *What dimensions are your 4D array?*
  
```{r}
dim(my4Darray)
```
  
  b. *How could you subset a part of your array to a single 2D matrix? Create a working example.*
  
```{r}
my2Dmatrix2 <- my4Darray[ , , 2, 3]
```
  
  c. *How could you subset a part of your array to a single 3D array? Create a working example.*
  
```{r}
my3darray2 <- my4Darray[ , , , 3]
```

Turn in this RMD file.