---
title: "Assignment 3.2"
author: "Julia Nguyen"
date: "10/25/2024"
output:
  html_document:
    df_print: paged
subtitle: "CPSC 292 Section 02"
---

## Assignment 3.2 

```{r, include=TRUE}
# Loading required libraries

```

### Question 1

*Complete the following steps:*

 a.  *Create a function that will take an object `x` and return the results of the following calculation: 4x^4  - sin(3x) + 12.*

```{r, include=TRUE}

calculate_function <- function(x) {
  result <- 4 * x^4 - sin(3 * x) + 12
  return(result)
}


```

 b. *Use your function to calculate the result of ten random numbers. Store the results in another object.*
 
```{r, include=TRUE}

calculate_expression <- function(x) {
  result <- 4 * x^4 - sin(3 * x) + 12
  return(result)
}
random_numbers <- runif(10, min = 0, max = 50) 
results <- sapply(random_numbers, calculate_expression)



```

 c. *Does your function perform a vectorized calculation? How do you know?*
 
Not vectorized; function is operates on a single value of x and calculates based on that input. 
If it were vectorized, R could apply the x without needing a loop.

### Question 2

*Make a function that reports the area of a land mass in the islands data set. The user input should be the name of the land mass. Include a line of code that uses the function as an example.*

```{r, include=TRUE}
data("islands")

get_land <- function(land_mass) {
  if (!(land_mass %in% names(islands))) {
    stop("Land mass not found in the islands dataset.")
  }
  area <- islands[land_mass]
  cat("The area of", land_mass, "is:", area, "thousand square miles.\n")
  
  return(area)
}

```

### Question 3

*Make a function that reports a correlation value between two values in the Harman23.cor covariation matrix. The inputs should be two values in the covariance matrix. Include a line of code that uses the function as an example.*

```{r, include=TRUE}
data("Harman23.cor")


get_correlation <- function(var1, var2) {
  cov_matrix <- Harman23.cor$cov
  
  if (!(var1 %in% rownames(cov_matrix)) || !(var2 %in% rownames(cov_matrix))) {
    stop("One or both variables not found in Harman23.cor covariance matrix.")
  }

  cov_value <- cov_matrix[var1, var2]
  sd_var1 <- sqrt(cov_matrix[var1, var1])
  sd_var2 <- sqrt(cov_matrix[var2, var2])
  
  correlation <- cov_value / (sd_var1 * sd_var2)
}

```

