---
title: "Assignment 1.13"
author: "Julia Nguyen"
date: "09/16/2024"
output:
  html_document:
    df_print: paged
subtitle: 'CPSC 292 Section 02'
---

### Collaboration team: 

Record who you've worked on the assignment with here. 


## Assignment 1.13 -- Class coercion

```{r setup, include=FALSE}
# Do not alter this section of code!
knitr::opts_chunk$set(echo = TRUE)
```

Write a R code in each chunk (gray space) that provides answers to the following questions. If any questions need direct answers, give them in regular text space (white space).

### Question 1

*Load the data set InsectSprays.*

```{r}
data("InsectSprays")
```

*Use it to answer the following questions.*

  a. *Convert the spray column to a numeric vector.*

```{r}
numeric <- as.numeric(InsectSprays$spray)
```
  
  b. *Convert the spray column to a characters vector.* 
  
```{r}
Character_spray <- as.character(InsectSprays$spray)
```
  
  c. *Convert the count column into an integer vector.*
  
```{r}
Integar_spray <- as.integer(InsectSprays$count)
```

  d. *Use any mathematical expression with a comparison operator to convert the count column into a logical vector.*
  
```{r}
Spray_logical <- InsectSprays$count > 5
```

  e. *Convert the logical vector in part d into a numeric vector.*
  
```{r}
count_numeric <- as.numeric(Spray_logical)
```

### Question 2

*Load the data set state. This is a series of 5 vectors of different lengths and compositions (state.abb, state.area, state.division, state.name, state.region), 1 matrix (state.x77), and 1 list (state.center). Make these all into a single list with 7 members called state.info Make sure that each member of the list has a name.*

```{r}
data("state")
state.info <- list(abb = state.abb,area = state.area, division = state.division,name = state.name,region = state.region,x77 = state.x77,center = state.center)
```


### Question 3

*Can you convert state.info into a data frame? If so, write the code. If not, explain why.*
No, because state.info contains multiple types of data: vectors, a list, and a matrix. A data frame requires each column has the same length, but state.info (the list, vectors, and matrix) doesn't have consistent length. 

Turn in this RMD file.