---
title: "Assignment 1.14"
author: "Julia Nguyen"
date: "09/18/2024"
output:
  html_document:
    df_print: paged
subtitle: 'CPSC 292 Section 02'
---

### Collaboration team: 

Record who you've worked on the assignment with here. 


## Assignment 1.14 -- 

```{r setup, include=FALSE}
# Do not alter this section of code!
knitr::opts_chunk$set(echo = TRUE)
```

Write a R code in each chunk (gray space) that provides answers to the following questions. If any questions need direct answers, give them in regular text space (white space).

Each subpart of code below has at least one error. Correct each error, write a short explanation of your fix, and turn in the corrected version of this script. The script should run cleanly using "Source" in a clean working environment.

### Question 1

```{r}
data("Loblolly")
```

  a. 

```{r}
mean(Loblolly$height)
```
  
  There was a mispelling. Insted of :obolluy, it should be Loblolly.
  
  b. 
  
```{r}
sd(Loblolly$height)
```
  
 h in height should be lowercased.
  
  c. 
  
```{r}
data(Loblolly)
Loblolly$seed <- as.numeric(Loblolly$Seed)
mean((Loblolly$seed))

```

  The dataset name is mispelled. It shouldn't be Lobolly but Loblolly.And it is not numeric or logical which will make it null. So I did str() to convert it to a numeric. 

  d. 
  
```{r}
sd(Loblolly$Age)
```

it is not std, but sd to find the standard deviation.

### Question 2
  
```{r}
vec1 <- c(3, 9, 10, 3, 29)
mean(vec1)
```

I switched the order of the code. You can't do mean(vec1) because it hasn't existed yet.

### Question 3

```{r}
data("ChickWeight")
```

  a. 
  
```{r}
chick1.dat <- subset(ChickWeight, (ChickWeight$Diet==1))

```
  
It is missing the closing parenthesis at the end of the function  
  b. 
  
```{r}
chick1.dat <- subset(ChickWeight, ChickWeight$Diet==2)
```
  
It needs two = inside the function  
  c. 
  
```{r}
mean(ChickWeight$weight[ChickWeight$Time==0])
```
  
The need barracks not parenthesis because you use [] to access a specific column in a data frame or to subset  vectors. 

Turn in this RMD file.